\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex

The field of consumer-oriented augmented reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data. As the technology
progresses, several disparate industries have found novel uses for it, some
becoming extremely profitable~\autocite{webster2018}. With smartphone
manufacturers investing billions into AR technology~\autocite{mason2016}, it
seems poised to be the next big digital interface.

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. This technology can provide
accessible information to tourists and art viewers that they would not be able
to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto, is the
perfect example of a site that would benefit from AR~\autocite{bornoff2000}.
Kinkaku-ji is a UNESCO World Heritage Site~\autocite{unesco} and one of the
most popular tourist destinations in Japan~\autocite{japanguide2019}. The
Golden Pavilion is a magnificent sight to behold, but the gardens and grounds
are the true beauty of Kinkaku-ji. It is a living masterpiece of Zen Buddhist
landscape design, expanding on the natural beauty of Kyoto's forests and
mountains through the practice of borrowed scenery~\autocite{kuitert2002}.

However, much of the historic information at the site is lost on visitors
because it is not readily available to non-Japanese speakers. What few signs and
displays exist are presented only in Japanese, and do not provide most of the
history and context necessary to fully understand Kinkaku-ji.

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. The experience of walking through the site is enhanced by
informative narration and AR pop-ups that do not alter the buildings or ground
in real life.

@@

Many of the existing applications using AR, in our eyes, do not leverage the
full potential of this emerging technology. As with any new field, our
understanding of AR and how to develop for it is limited. All sorts of
different challenges and limitations face the development and production of AR
apps. Here are some that we considered when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they are
primarily used for minor spectacles and simple
tricks~\autocite{theappsolutions2018}. For example, one of the most popular
apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
Pokémon on top of a camera's video feed. Disappointingly, it does not interact
with anything around it. It just floats a fixed distance away from the user.

@@

@@

Despite these issues our team is happy with the product we delivered to
Kyoto~VR. Selling ARuko on app stores was not within the scope of our academic
project, but we were able polish the app enough such that it would be feasible
for Atticus to eventually sell the app. The UI could use more testing with real
users to make sure it is intuitive and easy to use. We also intended to add a
feature where the app could automatically download tour files from the Editour
server and import them without having to rebuild. We were not able to complete
this feature due to time constraints, but it could easily be added because all
of ARuko's business logic is abstracted and generalized to support multiple
tours. Editour also already supports requesting and downloading the most recent
versions of tours.

>>>>

The field of consumer-oriented augmented reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data (see
Figure~\ref{fig:arExample}. As the technology progresses, several disparate
industries have found novel uses for it, some becoming extremely
profitable~\autocite{webster2018}. With smartphone manufacturers investing
billions into AR technology~\autocite{mason2016}, it seems poised to be the next
big digital interface.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{ar-example.jpg}
	% Note: you don't actually need the part in square brackets for the
	% caption, but if you omit it the regular caption text will be used for
	% the List of Figures entry.
	\caption[A virtual model of the solar system projected onto the real world
	using AR]{A virtual model of the solar system projected onto the real world
		using augmented reality~\autocite{tedx2016}}
	\label{fig:arExample}
\end{figure}

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. This technology can provide
accessible information to tourists and art viewers that they would not be able
to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto (see
Figure~\ref{fig:kinkakuji1}, is the perfect example of a site that would benefit
from AR~\autocite{bornoff2000}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-1.jpg}
	\caption[The Golden Pavilion]{The Golden Pavilion~\autocite{fan2018}}
	\label{fig:kinkakuji1}
\end{figure}

Kinkaku-ji is a UNESCO World Heritage Site~\autocite{unesco} and one of the
most popular tourist destinations in Japan~\autocite{japanguide2019}. The
Golden Pavilion is a magnificent sight to behold, but the gardens and grounds
are the true beauty of Kinkaku-ji. It is a living masterpiece of Zen Buddhist
landscape design, expanding on the natural beauty of Kyoto's forests and
mountains through the practice of borrowed scenery~\autocite{kuitert2002}.

However, much of the historic information at the site is lost on non-Japanese
speaking visitors because it is often only available in Japanese. In addition to
the language barrier, the information provided does not include most of the
history and context necessary to fully understand Kinkaku-ji.

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
would disturb the buildings or grounds of a historic site our app does not rely
on these markers. Instead, ARuko recognizes images of objects that are already
at the site, and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
details.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{ar-marker.jpg}
	\caption[Augmented reality markers]{Augmented reality
		markers~\autocite{jeriaska2010}}
	\label{fig:arMarker}
\end{figure}

@@

Most existing applications using AR, in our team's opinions, do not leverage the
full potential of this emerging technology. As with any new field, our
understanding of AR and how to develop for it is limited. All sorts of different
challenges and limitations face the development and production of AR apps. In
this section we discuss some of the challenges we faced when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they
primarily revolve around deploying gimmicks~\autocite{theappsolutions2018}. For
example, one of the most popular apps to use AR, \textit{Pokémon Go}, primarily
uses its AR feature to place a Pokémon on top of a camera's video feed.
Disappointingly, it does not interact with anything around it. It just floats a
fixed distance away from the user.

@@

On a similar note, the requirements and scope of the project changed greatly
from week to week, and sometimes even within one day. We spent a significant
amount of time exploring concepts and features that were completely unrelated to
the final product. We also did not receive official specifications, such as the
design of the GUI Atticus wanted for the app, until very late in the development
process.

@@

We had some initial trouble getting started with Unity. Different versions of
Unity do not play well with each other. As a result, we often ran into bugs on
older hardware, such as the laptops we had to work with. Furthermore, a stable
version of the Unity editor is not available on GNU/Linux~\autocite{best2019},
so one of our team members had to install macOS in order to use it. We were able
to resolve these issues in the first weeks of the project, but it consumed some
of our valuable time in July.

\subsubsection{What Went Well}
\label{sec:whatWentWell}

Despite these issues, in the end we were able to create a useful working
prototype. The Editour is fully featured with everything needed to build an
audio tour anywhere in the world. ARuko allows users to experience useful
AR-enhanced tours in a pleasant and intuitive way. Together they provide a
complete platform for building augmented reality tour guide apps.

Our team's broad range of skills made it so that each member had specific tasks
that they were good at. This made the division of labor easier, and throughout
the project we never had issues splitting up work.

Editour was not initially a requirement that Atticus had in mind, but it turned
out to be a very useful tool in designing tours and allowing the app to be
extensible. Two members of our team, Cole Granof and Joseph Petitti, had
experience building web applications with HTML, CSS, and JavaScript, and the
Editour allowed them to use these skills to help the project.

The research time we put in at the beginning of the project also proved to be
very useful. Our decision to use Unity Vuforia based on this research made
implementing many of the complex AR features easier later on. If we had chosen a
less-ideal platform, we might have had to switch to a different one after
wasting time on that poor decision.

\subsubsection{Future Work}
\label{sec:futureWork}

Although selling ARuko on app stores was not within the scope of our academic
project, but we were able polish the app enough such that it would be feasible
for Atticus to eventually sell the app. The UI could use more testing with real
users to make sure it is intuitive and easy to use. We also intended to add a
feature where the app could automatically download tour files from the Editour
server and import them without having to rebuild. We were not able to complete
this feature due to time constraints, but it could easily be added because all
of ARuko's business logic is abstracted and generalized to support multiple
tours. Editour also already supports requesting and downloading the most recent
versions of tours.
